---
title: "workout01-sophia-johng"
author: "Sophia Johng"
date: "October 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing ggplot2 package
```{r}
library(ggplot2)
library(readr)
library(dplyr)
```

## Ranking of Teams 

#### Ranking by Salary
```{r}
teams <- read.csv("../data/nba2018-teams.csv")
teams <- arrange(teams,desc(teams$salary))

ggplot(teams,aes(x= reorder(team,salary),y=salary)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_hline(yintercept = sum(teams$salary)/length(teams$salary),color = "pink", size = 1.5) +
  labs(x = "Team",y = "Salary (in millions)",title = "NBA Teams ranked by Total Salary")
```

#### Ranking by Total Points 
```{r}
teams <- arrange(teams,desc(teams$points)) 

ggplot(teams,aes(x=reorder(team,points),y=points)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_hline(yintercept = sum(teams$points)/length(teams$points), color = "purple", size = 1.5) +
  labs(x = "Team", y = "Total points", title = "NBA Teams ranked by Total Points")
```

#### Ranking by Efficiency
```{r}
teams <- arrange(teams,desc(teams$efficiency)) 

ggplot(teams,aes(x=reorder(team,efficiency),y=efficiency)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_hline(yintercept = sum(teams$efficiency)/length(teams$efficiency),color = "blue", size = 1.5) +
  labs(x = "Team",y = "Efficiency",title = "NBA Teams ranked by Effiency")
```

#### Ranking by Percentage of 3-Pointers as a measure of Shooting skill

* This index would, theoretically, measure a team's shooting skills. As 3-pointers are typically more difficult to make than the other shots, the team that has a larger percentage of 3-pointers out of total scored points should theoretically players that are better shooters.

```{r}
points3_percent <- ((teams$points3/teams$points) * 100)
teams <- mutate(teams,points3_percent)

teams <- arrange(teams,desc(teams$points3_percent))

ggplot(teams,aes(x=reorder(team,points3_percent),y=points3_percent)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_hline(yintercept = sum(teams$points3_percent)/length(teams$points3_percent),color = "green", size = 1.5) +
  labs(x = "Team",y = "Percentage of 3-Pointers out of Total Points Scored",title = "NBA Teams ranked by Percentage of 3-Pointers")
```


## Comments and Reflections 

* This was my first time working on a project with such a file stucture. I feel pretty good about it; I definitely understand the reasoning of having such a file structure.
* This was not my first time using relative paths. 
* This was not my first tiem using R scipt.
* I thought creating the teams data frame was difficult. It took a bit to figure out the correct syntax and commands. I thought creating the .txt and .csv files was relatively simple.
* I did this assignment on my own. It took me about 3 hours to complete. The most time consuming part was creating the bar graphs. 
`